Drivers of sex differences in consumption

### 2017-07-05 sex-difference/sex-medicare-display.Rmd
sex medicare split

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=7, fig.height=4, fig.path='fig/', dev=c('png', 'pdf'),
                      echo=FALSE, warning=FALSE, message=FALSE, cache=TRUE, autodep=TRUE)
```

@@

# healthcare usage by sex
hc_by_sex = read_tsv('tbl_hc_by_sex.tsv')
hc_use_ratio = hc_by_sex %>% mutate(ratio=mean_n_days/min(mean_n_days)) %$% max(ratio)
```

@@

# fraction of risk ratio explained
frre = function(res, tm='is_femaleTRUE') {
  rr0 = res %>% filter(model=='base', term==tm) %$% exp(estimate)
  rr1 = res %>% filter(model=='expl', term==tm) %$% exp(estimate)
  (rr0 - rr1) / (rr0 - 1)
}

@@

Adding UTI to the model explained `r pct_show(frre(cipro_results))` of the increased mean ciprofloxacin consumption associated with being female.

@@

The nitrofurantoin model doesn't explain as much of the difference (`r pct_show(frre(nitro_results))`), which is maybe not surprising or troubling because nitrofurantoin is mainly prescribed to women. We're not confused about why this consumption is higher.

@@

But we do a bad job: `r pct_show(frre(azithro_results))` gets explained by COPD and respiratory complaints.

@@

```{r consumption_by_age_and_sex}
read_tsv('data/tbl_consumption_age_sex.tsv') %>%
  ggplot(aes(x=age, y=n, group=is_female)) +
  geom_boxplot()
```

>>>>

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=7, fig.height=4, fig.path='fig/', dev=c('png', 'pdf'),
                      echo=FALSE, warning=FALSE, message=FALSE, cache=FALSE)
```

@@

# healthcare usage by sex
hc_by_sex = read_tsv('data/tbl_hc_by_sex.tsv')
hc_use_ratio = hc_by_sex %>% mutate(ratio=mean_n_days/min(mean_n_days)) %$% max(ratio)
```

@@

# fraction of coefficient explained
fce = function(res, tm='is_femaleTRUE') {
  den = res %>% filter(model=='base', term==tm) %$% estimate
  num = res %>% filter(model=='expl', term==tm) %$% estimate
  1 - num/den
}

@@

Adding UTI to the model explained `r pct_show(fce(cipro_results))` of the increased mean ciprofloxacin consumption associated with being female.

@@

The nitrofurantoin model doesn't explain as much of the difference (`r pct_show(fce(nitro_results))`), which is maybe not surprising or troubling because nitrofurantoin is mainly prescribed to women. We're not confused about why this consumption is higher.

@@

But we do a bad job: `r pct_show(fce(azithro_results))` gets explained by COPD and respiratory complaints.

@@

```{r consumption_by_age_and_sex}
read_tsv('data/tbl_consumption_age_sex.tsv') %>%
  ggplot(aes(x=factor(age), y=n, color=is_female)) +
  geom_boxplot()
```
